Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-08 draft.tex
typos

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
\]
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) \ar[d] \\
\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d] \\
\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d]\\
\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
\end{tikzcd}
\]
The first map projects onto the $\Sym^0$ component of $\clie^\bu$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
Finally, the third map is induced by the extension of compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
\end{dfn}

>>>>

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
\]
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) \ar[d] \\
\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d] \\
\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d]\\
\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
\end{tikzcd}
\]
The first map evaluates the unit in $\Sym\left(\fg \otimes \Omega^\bu(U)\right)$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
Finally, the third map is induced by the extension of compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
\end{dfn}
